---
title: "R to Github"
output: html_document
---

<script type="text/javascript" src="../utils/menu.js"></script>

### A Sample Page

This page is here as a sample of what a page of analysis would look like in the final site. This (simple) example uses the `iris` dataset.

### Loading the Data

```{r include=FALSE}
knitr::opts_chunk$set(message=FALSE, warning=FALSE)
```

```{r}
library(tidyverse)

```

#### Linear Relationships

Let's look at a plot of these variables and their correlation.

```{r}
ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width)) + 
  geom_line() +
  ggtitle(paste0("Sepal Width vs. Sepal Length, r = ", cor(iris$Sepal.Length, iris$Sepal.Width)))
```

There doesn't seem to be a very good relationsthip. But what about sepal and petal lengths?

```{r}
ggplot(iris, aes(x = Sepal.Length, y = Petal.Length)) + 
  geom_line() +
  ggtitle(paste0("Petal Length vs. Sepal Length, r = ", cor(iris$Sepal.Length, iris$Petal.Length)))
```

We see a much higher correlation between these two variables.